\documentclass[letterpaper,10pt]{article}

\usepackage[margin=1.1cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}

\pagenumbering{gobble}

\setlength\parindent{0pt}
\setlist[itemize]{
  label=\textendash, itemsep=-2pt, topsep=3pt, leftmargin=*
}
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\Large
}{}{0pt}{}[\titlerule ]
\titlespacing*{\section}{0pt}{10pt}{13pt}

% Definitions for resume %

\newcommand{\resumeSectionBegin}[1]{\section{#1}}
\newcommand{\resumeSectionEnd}{\vspace{3pt}}

\newcommand{\resumeItemBegin}{\vspace{1pt}}
\newcommand{\resumeItemEnd}{\vspace{10pt}}

\newcommand{\nameinfo}[5]{
  \begin{center}
  {\Huge\textsc{#1}}\vspace{2mm}\break
  \addtolength{\tabcolsep}{6pt} 
  \begin{tabular}{@{}c|c|c|c}
  #2 & #3 & #4 & #5
  \vspace{15pt}
  \end{tabular}
  \addtolength{\tabcolsep}{-6pt} 
  \end{center}
}

\newcommand{\resumeItemHeading}[4]{
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    {\large \textbf{#1}} & \textsl{#3}\vspace{3pt} \\
    {\large \textsl{#2}} & \textsl{#4} \\
  \end{tabular*}
}

\newcommand{\project}[1]{
  {\large \textbf{#1}}\vspace{1pt}
}

% Resume %

\begin{document}

\nameinfo{Sean Helm}{\textbf{seanhelm}.com}{\textbf{seanmdhelm}@gmail.com}{github.com/\textbf{seanhelm}}{linkedin.com/in/\textbf{seanhelm}}

% Experience %

\resumeSectionBegin{Experience}
  \resumeItemBegin
    \resumeItemHeading{Amazon}{Software Development Engineer}{Seattle, WA}{Apr 2019 -- Present}
    \begin{itemize}
      \item Automated AWS resource management needed for FBA applications to integrate with new view materialization platform.
      \item Ensured consistency across FBA applications by engineering workflow to ingest snapshots into DataWave and publish updates.
      \item Led all service scaling and operational readiness efforts to prepare for traffic doubling during Prime Day and holiday season.
      \item Identified a widespread data quality issue affecting sellers in Europe and designed a backfill process.
    \end{itemize}
  \resumeItemEnd
  \resumeItemBegin
    \resumeItemHeading{Capital One}{Software Engineer}{McLean, VA}{Sep 2018 -- Apr 2019}
    \begin{itemize}
      \item Architected a caching solution in Java/Spring for a big data platform to reduce latency for recently run Snowflake queries.
      \item Lowered operational costs by enabling lifecycle management for the underlying cache using Python and AWS Lambda.
      \item Rewrote the security layer for Spring microservices to use LDAP for user authentication.
      \item Built out infrastructure with Jenkins and Terraform to automate deployment of AWS resources for the cache microservice.
    \end{itemize}
  \resumeItemEnd
  \resumeItemBegin
    \resumeItemHeading{Alarm.com}{Software Engineering Intern}{McLean, VA}{Jun 2017 -- Aug 2017}
    \begin{itemize}
      \item Optimized home automation testing by implementing a Windows service in C\# for allocating device tests to available servers.
      \item Leveraged Ember.js to provide a user interface for the distributed testing service and to display real-time testing results.
      \item Created a REST API with ASP.NET Web API to expose the distributed testing service to the client.
    \end{itemize}
  \resumeItemEnd
  \resumeItemBegin
    \resumeItemHeading{Alarm.com}{Software Engineering Intern}{McLean, VA}{Jun 2016 -- Aug 2016}
    \begin{itemize}
      \item Automated a tedious process by building an API in C\# to efficiently update branding information on security panels.
      \item Implemented a caching system for account information to speed up the dealer site page load speed by 40-60\%.
      \item Developed a responsive, customer-facing tool to allow home owners to search for and verify local home security dealers.
    \end{itemize}
  \resumeItemEnd
\resumeSectionEnd

% Education %

\resumeSectionBegin{Education}
  \resumeItemBegin
    \resumeItemHeading{George Mason University}{Bachelor of Science in Computer Science; Major GPA: 3.38.}{Fairfax, VA}{May 2018}
  \resumeItemEnd
\resumeSectionEnd

% Projects %

\resumeSectionBegin{Projects}
  \resumeItemBegin
    \project{Music Genre Classification with Gradient Boosting}
    \begin{itemize}
      \item Applied XGBoost machine learning algorithm in Python to classify music genres using features extracted with LibROSA.
      \item Utilized Matplotlib to produce visualizations of various performance metrics to help improve the classification model.
    \end{itemize}
  \resumeItemEnd
  \resumeItemBegin
    \project{Reddit Sentiment Analysis}
    \begin{itemize}
      \item Filtered negative Reddit comments in real-time into MongoDB using TextBlob sentiment analysis.
      \item Created a user-friendly web application using Node.js, Express, and Vue.js to review newly extracted comments.
    \end{itemize}
  \resumeItemEnd
  \resumeItemBegin
    \project{Toxic Mushroom Deep Dive}
    \begin{itemize}
      \item Compared Scikit-learn machine learning algorithms in Python for predicting whether mushrooms were toxic or edible.
    \end{itemize}
  \resumeItemEnd
\resumeSectionEnd

\end{document}